A systematic search for transiting planets using \KT

### 2015-02-08 ms.tex
Adding some references

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars (cite something).
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level.
Results from the primary mission include the detection of planet
transits with depths as small as (XX) parts per million (cite Barclay).

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations (cite someone- Gilliland 11?).
Although they generally do not influence the ability to search for transiting
planets, larger systematic (noise shits) exist on different timescales.
One of the most serious of these is spacecraft pointing:
If the detector flat-field is not known \emph{exquisitely}, then
tiny changes to the relative illumination of pixels caused by a star's
motion in the focal plane (or caused by motion of the focal-plane
boresight or orientation relative to the celestial sphere) will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
\kepler\ Mission, observing approximately a dozen fields near the ecliptic
plane, each for 75 days at a time.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

@@

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission (Cite-Ricker 14).
\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

>>>>

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars (cite something).
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level.
Results from the primary mission include the detection of planet
transits with depths as small as 12 parts per million \citep{Barclay:2013}.

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not influence the ability to search for transiting
planets, larger systematic (noise shits) exist on different timescales.
One of the most serious of these is spacecraft pointing:
If the detector flat-field is not known \emph{exquisitely}, then
tiny changes to the relative illumination of pixels caused by a star's
motion in the focal plane (or caused by motion of the focal-plane
boresight or orientation relative to the celestial sphere) will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary
\kepler\ Mission, observing approximately a dozen fields near the ecliptic
plane, each for 75 days at a time.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

@@

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission \citep{Ricker:2014}.
\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.
